Waveform and Passive Beamforming Design for Intelligent Reflecting Surface-Aided Wireless Information and Power Transfer

### 2020-09-18 main.tex
:pencil: Add plots
:construction: Change noise unit to dBm

\begin{section}{Performance Evaluations}
	\begin{figure}
		\centering
		\def\svgwidth{\columnwidth}
		\import{assets/}{layout.pdf_tex}
		\caption{System layout}
		\label{fi:layout}
	\end{figure}
	To evaluate the performance of the proposed IRS-aided SWIPT system, we characterize and compare the average R-E regions under typical setups. Consider a large open space WiFi-like environment at a center frequency of 5.18 \si{\GHz} with reference bandwidth $B=1$ \si{\MHz}. As shown in Fig. \ref{fi:layout}, we assume the IRS moves along a horizontal line parallel to the AP-user path. Define the projection of the AP-IRS path onto the AP-user path as $d_H$ and let the distance from the IRS to the AP-user path be $d_V$. Denote $d_D$, $d_I$, $d_R$ as the length of direct, incident, reflective paths, such that $d_I=\sqrt{d_H^2+d_V^2}$, $d_R=\sqrt{(d_D-d_H)^2+d_V^2}$. We fix $d_D=15$ \si{\meter}, $d_V=2$ \si{\meter} and choose a reference $d_H=2$ \si{\meter}. For all channels, the path loss and fading parameters are obtained from IEEE TGn channel model D \cite{Erceg2004}, and we regard all channels as NLoS unless otherwise mentioned. Reference path loss is set to $L_0=-35$ \si{\dB} at $d_0=1$ \si{\meter}, and taps are modelled as i.i.d. random variables with normalized total power. We choose number of subbands $N=16$ as reference and assume no spatial correlation across all arrays. Rectenna parameters are taken as $k_2=0.0034$, $k_4=0.3829$, $R_{\text{ant}}=50$ \si{\ohm}. The average Effective Isotropic Radiated Power (EIRP) is fixed to $-36$ \si{\dBi} while the reference average noise power is $\sigma_n=-40$ \si{\dBm} at all subbands. We also assume 0 \si{\dBi} IRS element gain and 2 \si{\dBi} receive antenna gain. For the algorithm, the tolerance is $\epsilon=10^{-8}$, the number of candidates in the Gaussian randomization method is $Q=10^{3}$, and the R-E region is averaged over 200 channel realizations. In the R-E boundary, the leftmost point corresponds to WPT ($\rho=1$) where power can be allocated simultaneously to modulated and unmodulated waveform to maximize the average output DC current. On the other hand, the rightmost point corresponds to WIT ($\rho=0$) where the solution coincides with water-filling algorithm allocating all power to modulated waveform only. For a fair comparison, the $x$-axis of the plots has been normalized to per-subband rate.

@@

@@

	The influence of the average noise power on the average R-E region is investigated in Fig. \ref{fi:re_noise}. For a sufficiently large $N$, the R-E region is approximately concave for a high noise level and approximately convex for a low noise level. As a result, TS is preferred at low SNR while PS is preferred at high SNR.

@@

>>>>

\begin{section}{Performance Evaluations}
	\begin{figure}
		\centering
		\def\svgwidth{\columnwidth}
		\import{assets/}{layout.pdf_tex}
		\caption{System layout}
		\label{fi:layout}
	\end{figure}
	To evaluate the performance of the proposed IRS-aided SWIPT system, we characterize and compare the average R-E regions under typical setups. Consider a large open space WiFi-like environment at a center frequency of 5.18 \si{\GHz} with reference bandwidth $B=1$ \si{\MHz}. As shown in Fig. \ref{fi:layout}, we assume the IRS moves along a horizontal line parallel to the AP-user path. Define the projection of the AP-IRS path onto the AP-user path as $d_H$ and let the distance from the IRS to the AP-user path be $d_V$. Denote $d_D$, $d_I$, $d_R$ as the length of direct, incident, reflective paths, such that $d_I=\sqrt{d_H^2+d_V^2}$, $d_R=\sqrt{(d_D-d_H)^2+d_V^2}$. We fix $d_D=15$ \si{\meter}, $d_V=2$ \si{\meter} and choose a reference $d_H=2$ \si{\meter}. For all channels, the path loss and fading parameters are obtained from IEEE TGn channel model D \cite{Erceg2004}, and we regard all channels as NLoS unless otherwise mentioned. Reference path loss is set to $L_0=-35$ \si{\dB} at $d_0=1$ \si{\meter}, and taps are modelled as i.i.d. random variables with normalized total power. We choose number of subbands $N=16$ as reference and assume no spatial correlation across all arrays. Rectenna parameters are taken as $k_2=0.0034$, $k_4=0.3829$, $R_{\text{ant}}=50$ \si{\ohm}. The average Effective Isotropic Radiated Power (EIRP) is fixed to $-36$ \si{\dBm} while the reference average noise power is $\sigma_n=-40$ \si{\dBm} at all subbands. We also assume 0 \si{\dBi} IRS element gain and 2 \si{\dBi} receive antenna gain. For the algorithm, the tolerance is $\epsilon=10^{-8}$, the number of candidates in the Gaussian randomization method is $Q=10^{3}$, and the R-E region is averaged over 200 channel realizations. In the R-E boundary, the leftmost point corresponds to WPT ($\rho=1$) where power can be allocated simultaneously to modulated and unmodulated waveform to maximize the average output DC current. On the other hand, the rightmost point corresponds to WIT ($\rho=0$) where the solution coincides with water-filling algorithm allocating all power to modulated waveform only. For a fair comparison, the $x$-axis of the plots has been normalized to per-subband rate.

@@

	% N increase -> more to balance, tradeoff between subbands
	% FF channel -> closed form optimal IRS; FS channel -> tradeoff between subbands

@@

	The influence of the average noise power on the average R-E region is investigated in Fig. \ref{fi:re_noise}. It is noted that for a large number of subbands ($N=16$ in this case), the R-E region is approximately concave for a high noise level and approximately convex for a low noise level. Moreover, there exists a

	% This is because

	As a result, TS is preferred at low SNR while PS is preferred at high SNR.

	% sections -> waterfilling: \rho only vs joint

	% irs, low noise power, high received power  L+->high snr, rho vs other L, M: snr and nonlinearity
	% frequency selective less multipath loss less with FF IRS
	% Fix subband rate

@@

	\begin{figure}
		\centering
		\begin{adjustbox}{width=\linewidth}
			\input{assets/re_los.tex}
		\end{adjustbox}
		\caption{Average R-E region for IRS-aided NLoS and LoS channels}
		\label{fi:re_los}
	\end{figure}

	\begin{figure}
		\centering
		\begin{adjustbox}{width=\linewidth}
			\input{assets/re_irs.tex}
		\end{adjustbox}
		\caption{Average R-E region for adaptive, fixed and no IRS over $B = 10$ \si{\MHz}}
		\label{fi:re_irs}
	\end{figure}
